Machines are Among Us

### 2020-11-29 paper/main.tex
real references

\subsection{Among Us}
Among Us is a currently popular social deduction game,
where the "imposters" attempt to sabotage and kill all of the "crewmates". Crewmmates have
to complete tasks and figure out who the imposters are and eliminate them before the imposters
win.
At certain points in the game, after periods of no direct communication, players 
debate the roles of each individual based on information previously acquired through
their personal experience. At the end of this discussion, every player votes on a single
player to be eliminated. The player with the most votes is eliminated, and if there
is a tie, no one is voted out. We chose to emulate this game based on
the overall simplicity of the two roles and the requirement of communication
for either party to succeed. If the crew do not exchange information 
and all vote the same person, 
the vote could result in a tie or a crew being eliminated.
If the imposters do not bluff, the crew can easily spot the liars among the group. 
This provides ample room to explore and experiment with the communication between
the two opposing parties.
\subsection{Adverserial Networks}
Within this design space, there are adversarial parties working against each other.
In the deep learning realm, adversarial situations appear in adversarial examples
[https://arxiv.org/pdf/1412.6572.pdf] and within GANs (generative adversarial networks)
[https://proceedings.neurips.cc/paper/2014/hash/5ca3e9b122f61f8f06494c97b1afccf3-Abstract.html].
In particular, the latter often designs a contest between two neural networks, in the form
of a zero-sum game.
We build upon these concepts and foundations in our work.
\subsection{Multi-agent Communication}
Inherently, a social deduction game requires multiple agents to be trained and contested.
This has been explored within the deep learning problem space with multi-agent subproblems.
Both cooperative [https://arxiv.org/pdf/1602.02672.pdf] [https://arxiv.org/pdf/1605.06676.pdf] 
and adversarial [https://arxiv.org/pdf/1610.06918.pdf] communication has been experimented with,
showing that models can effective share and also selectively protect information.
We reference these approaches we generate active adversarial communication between 
neural network models.
\section{Approach}
\subsection{Deductive Situation}
\subsection{Modeling Interpretation and Communication}
\subsection{Zero-sum Target}
\subsection{Training Scheme}
\subsection{Challenges}

>>>>

\subsection{Among Us}
Among Us is a currently popular social deduction game,
where the "imposters" attempt to sabotage and kill all of the "crewmates". Crewmmates have
to complete tasks and figure out who the imposters are and eliminate them before the imposters
win.
At certain points in the game, after periods of no direct communication, players 
debate the roles of each individual based on information previously acquired through
their personal experience. At the end of this discussion, every player votes on a single
player to be eliminated. The player with the most votes is eliminated, and if there
is a tie, no one is voted out. We chose to emulate this game based on
the overall simplicity of the two roles and the requirement of communication
for either party to succeed. If the crew do not exchange information 
and all vote the same person, 
the vote could result in a tie or a crew being eliminated.
If the imposters do not bluff, the crew can easily spot the liars among the group. 
This provides ample room to explore and experiment with the communication between
the two opposing parties.
\subsection{Adverserial Networks}
Within this design space, there are adversarial parties working against each other.
In the deep learning realm, adversarial situations appear in adversarial examples~\cite{AdverserialEx} and within GANs (generative adversarial networks)
~\cite{NIPS2014_5ca3e9b1}
In particular, the latter often designs a contest between two neural networks, in the form
of a zero-sum game.
We build upon these concepts and foundations in our work.
\subsection{Multi-agent Communication}
Inherently, a social deduction game requires multiple agents to be trained and contested.
This has been explored within the deep learning problem space with multi-agent subproblems.
Both cooperative~\cite{DBLP:journals/corr/FoersterAFW16}~\cite{DBLP:journals/corr/FoersterAFW16a} 
and adversarial ~\cite{DBLP:journals/corr/AbadiA16} communication has been experimented with,
showing that models can effective share and also selectively protect information.
We reference these approaches we generate active adversarial communication between 
neural network models.
\section{Approach}
\subsection{Deductive Situation}
\subsection{Modeling Interpretation and Communication}
\subsection{Zero-sum Target}
\subsection{Training Scheme}
\subsection{Challenges}
